iterSim

### 2022-12-15 analyses/plotterScript.Rmd
re-analyzed

  allModels<-data.frame(model=c("Null model","Cox_Lin",'CB_Logi','DeepSurv',
                                'DeepHit','PMNN_Spline','PMNN_Poly','Optimal',
                                "dsm"),
                        color=qualitative_hcl(9,palette='Dark 3'),
                        trueName=c("KM","Cox",'CBLR','DeepSurv',
                                'DeepHit','PMNN_Spline','CBNN','Optimal',
                                "DSM"))
  allModels$color[1]="#bfc1c2"
  allModels$color[2]="#FFED11"#"#7C4C74"
  allModels$color[3]= "#80471C" #"#F9A602"
  allModels$color[5]="#FF00AB"
  allModels$color[8]="#000000"
  allModels$color[9]="#8077D5"
 allModels<- allModels[order(allModels$trueName),]
    i <- sapply(metricSummary, is.factor)
    metricSummary[i] <- lapply(metricSummary[i], as.character)
    metricSummary<-metricSummary[complete.cases(metricSummary), ]
    mainTitle<-""
    metricSummary$color<-NA
    for(i in 1:nrow(metricSummary)){
      modelPos<-which(metricSummary$model[i] ==allModels$model)
      metricSummary$model[i]<-allModels$trueName[modelPos]
      metricSummary$color[i]<-allModels$color[modelPos]

@@

    if(method=="C-Index"){
    method=expression("c-ipcw")
    }   
 metricSummary<- metricSummary[-which(metricSummary$model=="PMNN_Spline"),]
  #mainTitle<-paste(method,' : 95% P.I. over ', iterations, ' iterations',sep='')
  colnames(metricSummary)[1]<-"Models"
  a<-ggplot(data=metricSummary, aes(x=times,y=means,col=Models))+
    geom_line() +
    geom_ribbon(aes(ymin=cilower95,ymax=ciupper95,fill=Models),linetype=0,alpha=0.3) +
    ggtitle(mainTitle) + 
    xlab(xlab) +
    ylab(method)+
    theme_minimal()+
    scale_color_manual(values=allModels$color[colorsToUse])+
    scale_fill_manual(values=allModels$color[colorsToUse])
   # scale_color_manual(labels = metricSummary$model, values = metricSummary$color)

@@

>>>>

  allModels<-data.frame(model=c("Null model","Cox_Lin",'CB_Logi','DeepSurv',
                                'DeepHit','PMNN_Spline','PMNN_Poly','Optimal',
                                "dsm"),
                        color=qualitative_hcl(9,palette='Dark 3'),
                        trueName=c("KM","Cox",'CBLR','DeepSurv',
                                'DeepHit','CBNN_Spline','CBNN','Optimal',
                                "DSM"))
  allModels$color[1]="#bfc1c2"
  allModels$color[2]="#FFED11"#"#7C4C74"
  allModels$color[3]= "#80471C" #"#F9A602"
  allModels$color[5]="#FF00AB"
  allModels$color[8]="#000000"
  allModels$color[9]="#8077D5"
 allModels<- allModels[order(allModels$trueName),]
    i <- sapply(metricSummary, is.factor)
    metricSummary[i] <- lapply(metricSummary[i], as.character)
    metricSummary<-metricSummary[complete.cases(metricSummary), ]
    mainTitle<-""
    metricSummary$color<-NA
    for(i in 1:nrow(metricSummary)){
      modelPos<-which(metricSummary$model[i] ==allModels$model)
      metricSummary$model[i]<-allModels$trueName[modelPos]
      metricSummary$color[i]<-allModels$color[modelPos]

@@

    if(method=="C-Index"){
    method=expression("c-ipcw")
    }   
 metricSummary#<- metricSummary[-which(metricSummary$model=="PMNN_Spline"),]
  #mainTitle<-paste(method,' : 95% P.I. over ', iterations, ' iterations',sep='')
  colnames(metricSummary)[1]<-"Models"
  a<-ggplot(data=metricSummary, aes(x=times,y=means,col=Models))+
    geom_line() +
    geom_ribbon(aes(ymin=cilower95,ymax=ciupper95,fill=Models),linetype=0,alpha=0.3) +
    ggtitle(mainTitle) + 
    xlab(xlab) +
    ylab(method)+
    theme_minimal()+
    scale_color_manual(values=allModels$color[colorsToUse])+
    scale_fill_manual(values=allModels$color[colorsToUse])
   # scale_color_manual(labels = metricSummary$model, values = metricSummary$color)

@@

```{r plotoldmort,fig.height=6,fig.width=6}

BrierIPAList<-readRDS('results/100oldBrier.rds')

library(eha)

data("oldmort")

preData<-data.frame(sex=oldmort$sex,
                 civ=oldmort$civ,
                 ses=oldmort$ses.50,
                 birthplace=oldmort$birthplace,
                 ageAtDeath=oldmort$exit,
                 imrAtBirth=oldmort$imr.birth,
                 region=oldmort$region,
                 birthdate=oldmort$birthdate,
                 time=oldmort$exit-oldmort$enter,
                 status=as.numeric(oldmort$event))

#BrierIPAList[[1]]$times<-BrierIPAList[[1]]$times*(max(preData$time, na.rm = T)-min(preData$time, na.rm = T)) + min(preData$time, na.rm = T)
ipaSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
brierSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
ibsSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
ibsTable<-as.data.frame(matrix(data=NA,nrow=100,ncol=length(unique(BrierIPAList[[1]]$model))))
colnames(ibsTable)<-unique(BrierIPAList[[1]]$model)
count=1
for(sim in BrierIPAList){
  ipaSims<-cbind(ipaSims, sim$IPA)
  brierSims<-cbind(brierSims,sim$Brier)
  ibsSims<-cbind(ibsSims,sim$IBS)
  for(mod in colnames(ibsTable)){

#[which(ipaSummary$model %in% c("PMNN_Spline","Cox_Lin")),]
pdf(file="figures/oldResult.pdf")
ipa
dev.off()

colnames(preData)[ncol(preData)-1]<-'time'
colnames(preData)[ncol(preData)]<-'status'
data<-preData
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

pdf(file="figures/oldResult.pdf")
plot_grid(pt,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))#, legend
dev.off()

#myVars<-c('MK167','EGFR','PGR','ERBB2','Hormone treatment','radiotherapy','Chemotherapy','ER_positive','age at diagnosis','time','status')
#catVars<-c('Hormone treatment','radiotherapy','Chemotherapy','ER_positive','status')

#tab2 <- as.data.frame(print(CreateTableOne(vars = myVars, data = data, factorVars = catVars)))
#saveRDS(tab2,"figures/t1Metabric.rds")

#pdf("figures/t1metabric.pdf", height = 50*nrow(tab2), width = 200*ncol(tab2))
#grid.table(tab2)
#dev.off()
#rm(pt)

pdf(file="figures/oldResult.pdf")  
ipa
dev.off()
ipaO<-plotPerformance(ipaSummary,method="IPA",iterations=iteration  )

brierO<-plotPerformance(brierSummary,method="BS",iterations=iteration )
ibsO<-plotPerformance(ibsSummary,method="IBS",iterations=iteration )

cidxList<-readRDS('results/100oldcidx.rds')

cidxSummary<-statCalcSim(cidxSims)
cidxO<-plotPerformance(cidxSummary,method='C-Index',iterations=iteration  )
cidxO
```

```{r plotgbsg,fig.height=6,fig.width=6}

BrierIPAList<-readRDS('results/100gbsgBrier.rds')

gbsg<-survival::gbsg

colnames(gbsg)[10]<-"time"
preData<-gbsg[,-1]
#preData$time<-preData$time+runif(nrow(preData),0,1)/100000000

data<-as.data.frame((model.matrix(~.,preData)[,-1]))

data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

#BrierIPAList[[1]]$times<-BrierIPAList[[1]]$times*(max(preData$time, na.rm = T)-min(preData$time, na.rm = T)) + min(preData$time, na.rm = T)
ipaSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
brierSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
ibsSims=data.frame(model=BrierIPAList[[1]]$model,times=BrierIPAList[[1]]$times)
ibsTable<-as.data.frame(matrix(data=NA,nrow=100,ncol=length(unique(BrierIPAList[[1]]$model))))
colnames(ibsTable)<-unique(BrierIPAList[[1]]$model)
count=1
for(sim in BrierIPAList){
  ipaSims<-cbind(ipaSims, sim$IPA)
  brierSims<-cbind(brierSims,sim$Brier)
  ibsSims<-cbind(ibsSims,sim$IBS)
  for(mod in colnames(ibsTable)){

#[which(ipaSummary$model %in% c("PMNN_Spline","Cox_Lin")),]
pdf(file="figures/gbsgResult.pdf")
ipa
dev.off()

colnames(preData)[ncol(preData)-1]<-'time'
colnames(preData)[ncol(preData)]<-'status'
data<-preData
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

pdf(file="figures/gbsgResult.pdf")
plot_grid(pt,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))#, legend
dev.off()

#myVars<-c('MK167','EGFR','PGR','ERBB2','Hormone treatment','radiotherapy','Chemotherapy','ER_positive','age at diagnosis','time','status')
#catVars<-c('Hormone treatment','radiotherapy','Chemotherapy','ER_positive','status')

#tab2 <- as.data.frame(print(CreateTableOne(vars = myVars, data = data, factorVars = catVars)))
#saveRDS(tab2,"figures/t1Metabric.rds")

#pdf("figures/t1metabric.pdf", height = 50*nrow(tab2), width = 200*ncol(tab2))
#grid.table(tab2)
#dev.off()
#rm(pt)

pdf(file="figures/gbsgResult.pdf")  
ipa
dev.off()
ipaO<-plotPerformance(ipaSummary,method="IPA",iterations=iteration  )

brierO<-plotPerformance(brierSummary,method="BS",iterations=iteration )
ibsO<-plotPerformance(ibsSummary,method="IBS",iterations=iteration )

cidxList<-readRDS('results/100gbsgcidx.rds')

cidxSummary<-statCalcSim(cidxSims)
cidxO<-plotPerformance(cidxSummary,method='C-Index',iterations=iteration  )
cidxO
```

### 2022-12-15 analyses/simpleSim.Rmd
re-analyzed

---
title: "Metabric"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

```{r,eval=T}

@@

```{python,eval=T}

import os
os.environ["CUDA_DEVICE_ORDER"] = "PCI_BUS_ID" 
os.environ["CUDA_VISIBLE_DEVICES"] = ""
#os.environ["OM_NUM_THREADS"]="2"

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_metabric<-T
pycox<-reticulate::import("pycox")
source_python('src/getMetabricData.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0
epo=as.numeric(params$epo)
patience = as.numeric(params$patience)
iteration=as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

```{r modelsMETABRIC,eval=eval_metabric}

start_time <- Sys.time()

#pycox<-reticulate::import("pycox")
#numpy<-reticulate::import("numpy")
#a<-pycox$datasets$metabric$read_df
#b<-numpy$asarray(a)

############################
###Data clean and prep
############################

metabric<-getMetabric()
colnames(metabric)[ncol(metabric)-1]<-'time'
colnames(metabric)[ncol(metabric)]<-'status'
data<-as.data.frame(model.matrix(~.,metabric)[,-1])
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

@@

  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )

############################
###Prep Loop
############################
BrierIPAList<-list()
cScore<-list()
pos<-1

@@

  ############################
  ###Bootstrap samples
  ############################  
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  sds<-sapply(train, function(x) (sd(x)))
means<-sapply(train, function(x) (mean(x)))
test<-normalizer(res$test,means,sds)[,-c(ncol(data))]
fullTest<-normalizer(res$test,means,sds)
val<-normalizer(res$validate,means,sds)

train<-normalizer(train,means,sds)

@@

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    next
  }
  dsmSurv<-as.data.frame(dsmSurv)
  colnames(dsmSurv) <-times
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

@@

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

@@

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly,
                 dsmSurvProper
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(11,10)]
  et_test<-as.matrix(fullTest[,c(11,10)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly','dsm')
  cScoreTemp[,1]<- tempTims

@@

  saveRDS(BrierIPAList,'results/100MetaBrier.rds')
  saveRDS(cScore,'results/100Metacidx.rds')
  pos=pos+1
} 
end_time <- Sys.time()

end_time-start_time

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()

@@

sessionInfo()

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

```{python}

import os
os.environ["CUDA_DEVICE_ORDER"] = "PCI_BUS_ID" 
os.environ["CUDA_VISIBLE_DEVICES"] = ""

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

easysim<-T
numSamp<-2000
```

```{r easySimpletests,eval=easysim}
start_time <- Sys.time()

  #############################
  ###Data generation
  #############################

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 1,z2=1,z3=1),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]

@@

numSamp<-nrow(trainOG)

BrierIPAList<-list()
cScore<-list()

pos<-1

@@

  #############################
  ###Data generation
  #############################

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 0.5,z2=0.5,z3=0.5),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]
  train<-data
  #test<-data[-samp,-c(ncol(data))]
  #fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )

@@

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    next
  }
  colnames(dsmSurv) <-times
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

  ##########################
  ###casebase optimal model
  ##########################
  final_mod_cb_glm <- fitSmoothHazard(status~z1+z2+z3,#z1:z2:z3+z1+z2+z3,+z1:z3+z1:z2:z3
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

  summary(final_mod_cb_glm)
  tglmAbsRisk<-absoluteRisk(final_mod_cb_glm,time=times,newdata=test,type="CI")
  tglmAbsRisk<-as.data.frame(tglmAbsRisk)
  rownames(tglmAbsRisk)<-tglmAbsRisk$time
  trueGlmProper<- t(tglmAbsRisk[-1,-1])

  class(trueGlmProper)<-c("tunnel",class(trueGlmProper))

@@

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ z1+z2+z3, data = train,x=T)

@@

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly))

  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                                  data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 trueGlmProper,
                 annProperpoly,
                 dsmSurvProper
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly','dsm')#,'dsm')
  cScoreTemp[,1]<- tempTims

@@

  saveRDS(BrierIPAList,'results/100easyBrier.rds')
  saveRDS(cScore,'results/100easycidx.rds')
  pos<-pos+1
}
end_time <- Sys.time()

@@
